---
title: "Tidying and Modeling Euteleostomi and Drosophila AA and NT Data"
output: html_document
theme: united
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
knitr::opts_chunk$set(echo = TRUE)
#figs.height,figs.width, setup in curly braces 
```

### Let's Try to Tidy `output_selectome/` Data!

So, what we're trying to do first is to merge all the .csv files in `output_selectome/` into one big .csv file. 
Then we're going to tidy that data, by tidying it by species, name, data type, and number of models. Maybe we'll add tidying parameters as we go along, but let's see!

Below will be some R code that's in the works, as of February 4th, 2020.

```{r}
csv_directory = "../output_selectome"
csv_files <- dir(path=csv_directory,pattern="*.csv")
# Reading in all the .csv files from `output_selectome/` directory
```

After reading in the data, we need to read the actual files. The code below is to read what's in the files and merge them into one data frame.

```{r}

csv_dataframe <- read_csv("../results/all_selectome_output_csvs.csv")
csv_dataframe
```

So I created a variable called `csv_dataframe` which includes all the csv files in one data frame. From here, I will be manipulating that data frame in the code below.

## Wrangle the Hell Out of this Data

So far, as of February 6th, 2020, I cleaned up the .csv by removing the variables `filename` and separating the `name` variable into `name` and `species` and deleting the transcription number that isn't needed. The ultimate goal for this .rmd is to create four separate plots separated by species and data type, so two Euteleostomi AA and NT and two Drosohpila AA and NT.

Let's try to gather the ic_type data now!

Ok, the ic_type data is now wrangled, with one column for the ic_type and and one column as the model. Time to rank the models, so then we can start plotting!


```{r}
csv_dataframe %>%
  separate (name,c("name","species","STOP"),sep="[.]") %>%
  dplyr::select(-filename,-STOP) %>%
  pivot_longer(AIC:BIC, names_to = "ic_type", values_to = "model") -> selected_models
selected_models
```

The data frame is now wrangled and tidied, by putting all the information criterions into its own column, and putting the corresponding model in its own column. 

Now, we're going to get the percentage of the top model being selected. There should only be six rows per each name because there are three information criterion per data type. 

```{r}
selected_models %>%
  group_by(name,species,datatype,ic_type) %>%
  mutate(total = n() )%>%
  ungroup() %>%
  group_by(name,species,datatype,ic_type, model) %>%
  mutate(n = n()) %>%
  mutate(percent_top_model = n/total) -> percent_selected_models 
percent_selected_models
```
  
With the top model percentage wrangled, this data can plotted against other data properties!

```{r}
### another tibble with total number of models per ictype/datatype/name/species
selected_models %>%
  group_by(name,species,datatype,ic_type) %>%
  mutate(total = n() ) %>%
  group_by(ic_type,model) %>%
  tally() %>%
  ungroup()
### Don't worry about this chunk yet, will work on it later
  #dplyr::select(-n) %>%
  ##rename(most_common_model = model)

  #group_by(name, number, ic_type) %>%
  #mutate(ic_rank = rank(ic_value)) %>%
  #filter(ic_rank == 1) %>%
  #ungroup() %>%
  #dplyr::select(name, number, Model, ic_type) 
  
```

## Let's Start Plotting!

### Number of Models per Dataset

Alright, so I have the selected models, and the top model percentage calculated. I'm now going to start  plotting separate datasets from the `selected_models` dataet. I will try to be finding dataset names that have multiple models selected for itself. I will also be looking for a dataset name that has one model selected for it by data type. 


```{r,include=FALSE}
selected_models

ex = "EMGT00050000000002"
#variable to filter the name for just this dataset, Drosophila 

selected_models %>%
  filter(name == ex,datatype=="NT") %>%
  ggplot(aes(x = model)) +
  theme_classic() +
  geom_bar(col="black",fill="firebrick", width=0.8) +
  facet_wrap(~ic_type) +
  theme(axis.text=element_text(size=6),plot.title=element_text(hjust=0.5)) +
  labs(x="Model",y="Number of Models per Alignment") +
  ggtitle("Drosophila NT Dataset 00050000000002")
  

selected_models %>%
  filter(name == ex,datatype=="AA") %>%
  ggplot(aes(x = model)) +
  theme_classic() +
  geom_bar(col="black",fill="slategray2", width=0.8) +
  facet_wrap(~ic_type) +
  theme(axis.text=element_text(size=6),plot.title=element_text(hjust=0.5)) +
  labs(x="Model",y="Number of Models per Alignment") +
  theme(axis.text.x=element_text(size=3))+
  ggtitle("Drosophila AA Dataset 00050000000002")


```


Holy cow! 10 models selected for this dataset, with 4 selected for the NT data type and 6 selected for the AA data type. 

As of February 11th, I have found a dataset that has 10 models selected for it. These plots are unfinished, but show the necessary information (number of models!). Will be prettying them up soon.

## How many models are selected for 

Time to start plotting total number of models per all datasets pertaining to specific species and data type (Euteleostomi or Drosophila and AA or NT)

The function below takes in three arguments. The first is the dataset that needs to be read in, the second is the indicated species, and the third is the indicated datatype. The data is wrangled in this function to indicate how many datasets are selected for 'n' amount of models.

```{r}

process_ggplot_ready_data <- function(dataset,a_species,a_datatype)
{
  dataset %>%
    filter(species==a_species,datatype==a_datatype)%>%
    group_by(name,model,ic_type,datatype) %>%
    tally() %>%
    ungroup() %>%
    select(-n) %>%
    group_by(name,ic_type) %>%
    tally() %>% 
    rename(number_datasets = n ) %>%
    group_by(number_datasets, ic_type) %>% 
    tally() %>% 
    rename(number_of_models = n) -> ready_data
  ready_data
  
}  

```

After the data is processed in the function above, it needs to be plotted. The function below plots data, with one argument, the ready data.

```{r}
plot_processed_alignments <- function(ready_data)
{


  ready_data %>%
  ggplot(aes(x=number_datasets,y=number_of_models,width=.86)) +
    geom_col() + 
    geom_text(aes(x = number_datasets, y = number_of_models + 1, label = number_of_models),size=3,hjust=.5,vjust=.01)+
    facet_wrap(~ic_type) + 
    xlab("Number of Datasets") +
    ylab("Number of Selected Models") +
    theme_linedraw()  +
    scale_x_continuous(breaks=seq(0,20,1))+
    theme(plot.title=element_text(hjust=0.5))-> plotted_data
  plotted_data
  
}

```
Below are the variables that are going to be used as arguments for our functions.


```{r}
flies <- "Drosophila"
bony<- "Euteleostomi"
amino<-"AA"
nuc<- "NT"
```

### Drosophila AA Number of Models

```{r}

dros_aa <-process_ggplot_ready_data(selected_models,flies,amino)
daa_plot <- plot_processed_alignments(dros_aa)

```

### Drosophila NT Number of Models

```{r,include=TRUE}
dros_nt <-process_ggplot_ready_data(selected_models,flies,nuc)
dnt_plot <- plot_processed_alignments(dros_nt)
```

### Euteleostomi AA Number of Models

```{r,include=TRUE}
eut_aa <-process_ggplot_ready_data(selected_models,bony,amino)
eaa_plot <-plot_processed_alignments(eut_aa)
```

### Euteleostomi NT Number of Models

```{r}
eut_nt <- process_ggplot_ready_data(selected_models,bony,nuc)
ent_plot <-plot_processed_alignments(eut_nt)
```


One color for aa and nt or one color for species 

percentage of the time that the GIVEN was the best model out of 50. 
do this 3x; for the 3 most common MODELS, for each criterion, for each aa/nt for each dros/eutel = 36 plots?. no more htan 6 plots in a grid. only applies when >= 3 models.

how do we do?
count( dataytpe, ictype, species, name, model)
#count is shortcut for groupby,tally, and ungroup()
filter for one, filter for two, filter for three
only do this for datasets that have three models, lots of wrangling!
start to wrangle on paper!!!!! 


mutate a new column, determine if it is the top model, then sum by group by, tally, model, rank
percentage of time the first one occurs

```{r,fig.height=8,fig.width=16}

(daa_plot|ent_plot|eaa_plot)/dnt_plot

```

Okay, so we're going to start doing more plotting!
We want to show the percentage of the time that the given was the best model out of 50. Need to do this 30 times, for the 3 most common models, for each criterion, for each aa/nt for each dros/eutl. No more than 6 plots in a grid. Only applies when dataset has 3 or more models. Let's start with `selected_models`.


```{r}
selected_models %>%
  count(datatype,ic_type,species,name,model) %>%
  rename(number_of_models=n) %>%
  filter(number_of_models>=3) %>%
  count(number_of_models) %>%
  tail()
 ```

filter() is a command that returns rows that match the arguments given. Note that dplyr is not yet smart enough to optimise filtering optimisation on grouped datasets that don't need grouped calculations. For this reason, filtering is often considerably faster on ungroup()ed data.
