---
title: "Plots Pertaining to Data Properties of Alignments"
author: "Molly Miraglia"
---
Hello, welcome to my R markdown file, this is example text.


```{r setup, include = FALSE}
library(tidyverse)
```
## Analysis of Data
Below, I have my csv file, named "one_csv.csv" read by R, and imported into the markdown. I will be using the file to create plots!

```{r, include = FALSE}
one_csv <- read_csv(file="one_csv.csv")
```

```{r}
one_csv
```
I will be running one_csv.csv through the function, ggplot, to create plots, from the tidyverse package.

Disclaimer: In my data, there is missing data, as there were errors creating trees.Therefore, the tidyverse function 'drop_na' has been used to remove "NA" from my plots.

#Plot One! - A Test!
```{r}
one_csv %>%
  drop_na %>%
  ggplot(aes(x =mean_seq_length, y = number_models)) + 
  geom_point(aes(color = data_type)) +
  scale_color_manual("Data Type",labels=c("aa","nt"),values=c('pink2','lightskyblue')) +
  theme(legend.key=element_rect(color="goldenrod", fill = "ivory1"),legend.background = element_rect(fill="pink", color = "grey")) +
  scale_x_continuous(name= "Mean Sequence Length") +
  scale_y_continuous(name="Number of Models per Dataset")
```

This plot can virtually be ignored, it was meant to be a test. I enjoyed picking out the colors though. Time for the real deal (faceting!)


#Plot Two - Starting to Facet!

The following plot will be beautiful.

```{r}
one_csv %>%
  drop_na() %>%
  ggplot(aes(x=mean_seq_length,y=number_models)) +
  geom_point() + 
  facet_grid(ic_type ~data_type)
```
Alright, so that plot has all the faceting it needs, but it's boring! Let's add colors and change around the axis titles and maybe even the legend! Perhaps I will even give the plot a title ohohhoh.


```{r}

one_csv %>%
  drop_na() %>%
  ggplot(aes(x=mean_seq_length,y=number_models)) +
  geom_point(aes(color=data_type)) + 
  facet_grid(ic_type ~data_type) +
  scale_x_continuous(name="Mean Sequence Length") +
  scale_y_continuous(name="Number of Models per Dataset") +
  scale_color_manual(labels=c("aa","nt"),values=c("palevioletred","cornflowerblue")) +
  theme(legend.key=element_rect(fill="ivory3")) +
  scale_fill_discrete(name="Data Type",breaks=c("aa","nt"),labels=c("Amino Acid Data","Nucleotide Data"))
  
  
```

Ok I've been trying to change the faceting labels, was using `labeller` function, but to no avail. Will be giving up now.




